Disparity peaks

### 2018-02-05 analyses/07-figure-peaks.Rmd
Change colours to viridis

```{r}
beck_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
        panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.background = element_blank()) +
  annotate("text", x = 1, y = 0.15, label = "Beck2012")

beck_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
        panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.background = element_blank())
```

@@

```{r}
brusatte_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
  expand_limits(y = 0) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none", 
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank())

brusatte_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
  expand_limits(y = 0) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none", 
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) 
```

@@

```{r}
bapst_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank())

bapst_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank())
```

@@

```{r}
wright_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 expand_limits(y = 480) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank())

wright_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 expand_limits(y = 480) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank()) 
```

>>>>

```{r}
beck_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
        panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_text(size = 12)) +
  geom_text(data = ann_text, aes(x = 1, y = 5, 
            label = "Beck2012"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1, end = 0.8)

beck_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
        panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.background = element_blank(),
        strip.text.x = element_text(size = 12)) +
 geom_text(data = ann_text, aes(x = 1, y = 5, 
            label = "Beck2012"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1, end = 0.8)
```

@@

```{r}
brusatte_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
  expand_limits(y = 0) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none", 
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank(),
       strip.text.x = element_text(size = 12)) +
 geom_text(data = ann_text, aes(x = 1, y = 5, 
            label = "Brusatte2014"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1, end = 0.8)

brusatte_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
  expand_limits(y = 0) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none", 
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank(),
       strip.text.x = element_text(size = 12)) +
 geom_text(data = ann_text, aes(x = 1, y = 5, 
            label = "Brusatte2014"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1, end = 0.8)
```

@@

```{r}
bapst_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank(),
       strip.text.x = element_text(size = 12)) +
 geom_text(data = ann_text, aes(x = 1, y = 5, 
            label = "Bapst2016"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1, end = 0.8)

bapst_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 # expand_limits(x = 0, y = c(0,1)) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank(),
       strip.text.x = element_text(size = 12)) +
 geom_text(data = ann_text, aes(x = 1, y = 5, 
            label = "Bapst2016"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1, end = 0.8)
```

@@

```{r}
wright_peaks <- 
  ggplot(data_max2_epoch, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 expand_limits(y = 480) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank(),
       strip.text.x = element_text(size = 12)) +
 geom_text(data = ann_text, aes(x = 1, y = 5, 
            label = "Wright2017"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1, end = 0.8)

wright_peaks_age <- 
  ggplot(data_max2_age, aes(y = time1, x = model, colour = model)) +
  theme_classic(base_size = 12) +
  geom_point() +
  geom_point(aes(y = time2, x = model, colour = model)) +
  facet_wrap(~bin_type, ncol = 3) +
  scale_x_discrete(labels = c("bins", "gradual", "proximity")) +
 expand_limits(y = 480) +
 theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "none",
       panel.spacing = unit(0, "lines"),
        panel.border = element_blank(),
        strip.text = element_blank(),
       strip.text.x = element_text(size = 12)) +
 geom_text(data = ann_text, aes(x = 1, y = 5, 
            label = "Wright2017"), col = "black") +
  scale_colour_viridis(discrete = TRUE, direction = -1, end = 0.8) 
```
